VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper_dedup.tex
revise

It should not be noted that one could consider 
to rely on filesystem features to provide more replication to popular
blocks, without the extra complexity of separating popular and non-popular
data. The main problem with this  approach is that without separating the
popular chunks from the less-popular, the popular chunks are dispersed across
all of the filesystem blocks in the storage system.  We would
have to add extra replication to each file block as long as it contains a popular chunk.

>>>>

%One could try to rely on filesystem features to 
If we do not separate the
popular chunks from the less-popular, the popular chunks are dispersed across
all of the filesystem blocks in the storage system.  Then we cannot leverage the file system features to 
provide extra replication to popular and shared chunks because  
we have to add extra replication to each file block as long as it contains a popular chunk.

### 2014-01-31 snapshot_system/paper_eval.tex
revise

\subsection{Settings}
We have performed a trace-driven study based on a production dataset~\cite{WeiZhangIEEE} from 
Alibaba Aliyun's cloud platform with about 2500 VMs, running on 100 physical machines. 
Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage system while
a user may instruct extra snapshots to be saved.
The VMs of the sampled data set use popular operating systems such as 
Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
%The backup of VM snapshots is required to complete within few  hours every night.
Each VM has about 40GB of storage  data  on average
including OS and user data disk.
The daily snapshot change rate is about 2-3\% on average.
%All data are divided into 2 MB fix-sized segments and 
The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
%Each segment is divided into 
%variable-sized content chunks with an average size of 4KB.
%Popularity of data blocks are collected through global counting and 
%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.

@@

Our results show that VC has a significantly  higher availability than VO as the number of
failed machines increases.
%Our VM-centric approach shows significant improvements
%in VM availability.
For example, with 3/100 machines failed and 25 VMs per machine, VO with 69.5\% availability could lose data in 763 VMs 
while VC with 99.7\% loses data for 8 VMs.
The key reason is that for most data in VC, only a single VM can be affected by
the loss of a single file block. Since most blocks contain chunks for a single
VM, VMs can depend on a smaller number of blocks, while in VO, the loss of a
single block tends to affect many VMs.
% because our VM-centric approach
%localizes deduplication.

Although the loss of a PDS block affects many VMs,
by increasing replication for those blocks we minimize the effect on VM
snapshot availability, and this is one of the key contributions of our
approach, the clear separation of highly popular data from less popular data.
%By having extra replicas for the PDS data, we reduce the failure rate of PDS
%FSBs enough that the failure rate for the VM approaches the failure rate of the
%Non-PDS blocks. This minimizes the drop in availability between the expected
%and worst case for VC.
%
%One of the advantages of VC is that there is a division between
%popular and non-popular data to facilitate improved reliability. 
Figure~\ref{fig:pds-replication} shows
the impact of increasing PDS data replication. 
While the impact on storage cost is small (because we have separated out only
the most popular blocks),
a replication degree of 6  has a significant improvement over 4. The
availability is very similar
for $r_c=6$ and $r_c=9$, and beyond $r_c=6$ improvements are minimal.

@@

\comments{ %replaced by table below to recuce space requirements
\begin{figure}[ht]
    \centering
    \begin{subfigure}%{.5\textwidth}
      \centering
      %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
            \begin{tikzpicture}
                    \begin{axis}[
                    tick label style={font=\scriptsize},
                    tick style=thin,
                    width=0.5\linewidth,
                    title={\small $p=100$},
                    cycle list={
                        {blue,thin,solid,mark=none},
                        {red,thin,densely dashed,mark=none},
                        {red,thin,densely dotted,mark=none}
                    },
                    xlabel={\tiny Failed nodes},
                    ylabel={\tiny Snapshot Availability (\%)},
                    %extra y ticks={99.9}, %if important numbers are missing
                    mark options=solid,
                    legend columns=-1,
                    legend style={
                        font=\small\sffamily,
                        cells={anchor=west}, %legend entry alignment
                        legend pos=south west %legend position
                    },
                    legend to name=legend:vm-availability,
                    %reverse legend,
                    ]
                    \addplot table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                    \addlegendentry{VO}
                    \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                    \addlegendentry{VC}
                    %\addplot table[x=NodesFailed,y=VCOpt1]{figures/node_failures_100.txt};
                    %\addlegendentry{VC (CDS ordering)}
                    \end{axis}
            \end{tikzpicture}
      %\caption{100 machine cluster.}
      \label{fig:vm-availability-100}
    \end{subfigure}%
    \begin{subfigure}%{.5\textwidth}
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
            %the expressions in this plot are simply to trick pgfplots into not expanding the y range, and don't actually change the data
            % expression used: (99.999+((y-99.999)*1000)/1000)
            \pgfplotsset{/pgf/number format/.cd,
                fixed,precision=4}
		\begin{axis}[
                    width=0.5\linewidth,
                    tick label style={font=\scriptsize},
                    tick style=thin,
		title={\small $p=1000$},
                %ymin=099.9991,
                %ymax=100.0002,
                %ytick=data,
                %yticklabels from table={figures/vm_availability_1000.txt}{[index]1},
                yticklabel={%this is a hack to get around the small yrange
                    \pgfmathfloatparse{99.999+\tick/1000}
                    \pgfmathprintnumber{\pgfmathresult}
                },
                cycle list={
                    {blue,thin,solid,mark=none},
                    {red,thin,densely dashed,mark=none},
                    {red,thin,densely dotted,mark=none}
                },
		xlabel={\tiny Failed nodes},
		ylabel={\tiny Snapshot Availability (\%)},
		%extra y ticks={99.99}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                %reverse legend,
		]
                %\addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_1000.txt};
                \addplot table[x=NodesFailed,y expr=(\thisrow{VO}-99.999)*1000]{figures/node_failures_1000.txt};
                %\addlegendentry{$VO\,6.3$ (optimistic)}
                %\addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_1000.txt};
                \addplot table[x=NodesFailed,y expr=(\thisrow{VC3}-99.999)*1000]{figures/node_failures_1000.txt};
                %\addlegendentry{$VC\,1250$ (estimated)}
                %\addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_1000.txt};
                \addplot table[x=NodesFailed,y expr=(\thisrow{VCWC1}-99.999)*1000]{figures/node_failures_1000.txt};
                %\addlegendentry{$VC\,2500000$ (worst-case)}
                %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                %\addlegendentry{$VO\,20$ (optimistic)}
		\end{axis}
	\end{tikzpicture}
        %\caption{1000 machine cluster.}
  \label{fig:vm-availability-1000}
\end{subfigure}
    \pgfplotslegendfromname{legend:vm-availability}
      \caption{Availability of VM snapshots for VO and VC when failed machines vary
from 1 to 40.  Non-PDS replication is fixed
at 3 and PDS replication is 6 \emph{THIS PLOT IS BEING REPLACED BY A TABLE} 
      }
      \label{fig:vm-availability}

\end{figure}
}
\begin{table}
  \centering
    \footnotesize
    \tabcolsep=0.11cm
    \pgfplotstabletypeset[
        comment chars=!,%use ! before a row in the data table to exclude it
        columns={NodesFailed,VO100,VC100,VO1000,VC1000},
        columns/NodesFailed/.style={
            column name={\multirow{3}{*}{Failures ($d$)}}
        },
        columns/VO100/.style={
            column name={
                \multicolumn{4}{c|}{VM Snapshot Availability(\%)}\\&
                \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
            VO},
            fixed, precision=6
        },
        columns/VC100/.style={
            column name={VC},
            fixed, precision=6},
        columns/VO1000/.style={
            column name={VO},
            fixed, precision=6},
        columns/VC1000/.style={
            column name={VC},
            fixed, precision=6},
        every head row/.style={
            before row={\hline},
            after row={\hline},
        },
        every last row/.style={after row=\hline},
        column type/.add={}{|},
        every first column/.style={column type/.add={|}{}},
        %the below rows can be used to extract rows 3,5,10,20 from rows 0-40
        %skip rows between index={0}{3},
        %skip rows between index={4}{5},
        %skip rows between index={6}{10},
        %skip rows between index={11}{20},
        %skip rows between index={21}{41}
    ]{figures/availability_table.txt}
    \caption{Availability of VM snapshots for VO and VC ($r_c=6$).}
    \label{tab:vm-availability}
\end{table}

\begin{figure}[htb]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=10,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{
                    VO,
                    $r_c=4$,
                    $r_c=5$,
                    $r_c=6$,
                    $r_c=9$
                }
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees}
  \label{fig:pds-replication}
\end{figure}

\comments{
\begin{figure}[htb]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=20,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                %\addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                %\addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{
                    %VO,
                    %$r_c=4$,
                    $r_c=5$,
                    $r_c=6$,
                    $r_c=9$
                }
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees \todo{decide which one}}
  \label{fig:pds-replication-old}
\end{figure}

}

\subsection{Deduplication Efficiency}
\label{sect:evaldedup}

\comments{
%this version combines the old and the minhash alg. to compare against srb
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            width=\linewidth,
            height=0.75\linewidth,
            cycle list={%
                {blue,solid,mark=square*},
                {blue,solid,mark=triangle*,mark size=1.5},
                {blue,solid,mark=diamond*,mark size=1.5},
                %{blue,solid,mark=pentagon*,mark size=1.4},
                {red,draw=red,dotted,mark=square},
                %{red,densely dotted,mark=triangle,mark size=1.5},
                %{red,densely dotted,mark=diamond,mark size=1.5},
                {brown,dashed,mark=*},
                %{red,densely dotted,mark=o},
                %{red,densely dotted,mark=pentagon,mark size=1.4},
            },
            mark repeat={10},
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            xmin=0,
            ymin=85,
            ymax=100,
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            legend columns=2,
            legend style={
                font={\tiny\sffamily},
                nodes={right}
                %at={(0.5,-0.2)},
                %anchor=north
            },
            ]
            \addplot table[x=VMs,y=MHcds4] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHcds2] {figures/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
            \legend{VC( $\sigma=4\%$),
                VC($\sigma=2\%$),
                %VC MH($\sigma=1\%$),
                VC(No PDS),
                %VC($\sigma=4\%$),
                VC($\sigma=2\%$\, No similarity guidance),
                %VC($\sigma=1\%$),
                SRB
            };
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication efficiency of VC and SRB.}
  \label{fig:exbin-efficiency-graph2}
\end{figure}

}

\begin{figure}[htb]
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                width=\linewidth,
                height=0.6\linewidth,
                ybar,
                bar width=0.5cm,
                ymax=98.7,
                enlarge x limits=0.15,
                style=thin,
                ylabel={Dedup. Efficiency (\%)},
                ytick={93,94,95,96,97,98},
                xtick=\empty,
                ymajorgrids,
                grid style=densely dotted,
                %symbolic x coords={VC-No PDS, VC-2\%PDS w/o similarity, VC-2\%PDS, VC-4\%PDS, SRB},
                %symbolic x coords={VC0, VC2N, VC2, VC4, SRB},
                %xticklabels from table={figures/efficiency_comparison_bars.txt}{alg}
                nodes near coords,
                every node near coord/.append style={
                    anchor=-145+\coordindex*10
                }
            ]
            %\addplot[fill=blue] coordinates {(VC0,93.02) (VC2N,94.31) (VC2,96.01) (VC4,96.58) (SRB,97.86)};
            %\addplot[fill=blue] coordinates { (VC-No PDS,93.02) (VC-2\%PDS w/o similarity,94.31) (VC-2\%PDS,96.01) (VC-4\%PDS,96.58) (SRB,97.86) };
            \addplot [%
                point meta=explicit symbolic,
                fill=blue
            ] table [x expr=\coordindex, y=efficiency,meta=alg] {figures/efficiency_comparison_bars.txt};
        \end{axis}
    \end{tikzpicture}
    \caption{Efficiency comparison between different VC settings and
        Stateless Routing with Binning}
    \label{fig:efficiency-comparison}
\end{figure}

Figure~\ref{fig:efficiency-comparison} shows the deduplication efficiency for SRB and VC using different settings,
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
that is the percent of duplicate chunks
which are detected and removed.
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB per machine
and  the deduplication efficiency can reach over 96\%.
When $\sigma=4\%$, the deduplication efficiency can reach 96.6\% while space consumption increases to 200MB per machine. 
%and  the deduplication efficiency can reach 96.489\%.
%When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
with a slight reduction in deduplication efficiency.

@@

Figure~\ref{fig:efficiency-comparison} also shows the efficiency of VC without local similarity search.
%There is a big efficiency drop in this curve when the number of VMs is about 30.
The reason similarity search provides such an improvement is that
%Without this (i.e. when we only 
there are VMs in which
data  segments are moved to another location on disk, for example when a file is rewritten
rather than modified in place,  
and a dirty-bit or offset-only based detection would not be able to detect such a movement.
We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently.
In general, adding local similarity-guided search increases deduplication efficiency from 94\% to over 96\%.
That is one significant improvement compared to the work in ~\cite{WeiZhangIEEE}
which uses the parent segment at the same offset to detect duplicates instead of similarity-guided search.
% In general, our experiments show that
% dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
% which leads about a 75.86\% reduction.
% Similarity-guided local search can further reduce the data size
% to about 12.05\% of original size, namely it delivers an additional 12.09\% reduction.
% The PDS-based global duplicate detection with $\sigma=2\% $
% can reduce the size further to 8.6\% of original size, namely it 
% delivers an additional 3.45\% reduction.

In general, our experiments show that
dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
which leads to about a 75.86\% reduction.
Similarity-guided local search can further reduce the data size
to about 12.05\% of original, namely it delivers a 50.08\% reduction to the dirty segments.
The popularity-guided global deduplication with $\sigma=2\% $
can reduce the data further to 8.6\% of its original size, so
it provides additional 28.63\% reduction to the remaining data.

@@

\begin{table}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Tasks & CPU & Mem &Read &  Write  & Time  \\ 
    & & (MB)          &(MB/s) &  (MB/s) & (hrs) \\ \hline
%    1     & 19\% & 118.1 & 50MB/s 8.37 & 1.314\\ \hline
    1     & 19\% & 118 & 50 & 16.4 & 1.31\\ \hline
%    2     & 35\% & 131.8 & 9.0 & 1.226\\ \hline
    2     & 35\% & 132 &50  & 17.6 & 1.23\\ \hline
    %4     & 63\% & 154.1 & 9.3 & 1.179\\ \hline
    4     & 63\% & 154&50   & 18.3 & 1.18\\ \hline
    6     & 77\% & 171.9 & 50 &  18.8 & 1.162\\ \hline
%    8     & 82\% & 90.5 & 89.2 & \\ \hline
%    10                      & 85\% & 97.2   & 90.4 \\ \hline
%    12                      & 91\% & 95.6    & 91.5 \\ \hline
    \end{tabular}
\caption{Resource usage of concurrent backup tasks at each machine}
\label{tab:resource_usage}
\end{table}

>>>>

\subsection{Settings}
We have performed a trace-driven study based on a production dataset~\cite{WeiZhangIEEE} from 
Alibaba Aliyun's cloud platform with about 2500 VMs, running on 100 physical machines. 
Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
system while a user may instruct extra snapshots to be saved.
Each VM has about 40GB of storage  data  on average
including OS and user data disk.
Each physical machine deals with about 10TB of snapshot data.
The VMs of the sampled data set use popular operating systems such as 
Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
%The backup of VM snapshots is required to complete within few  hours every night.
The daily snapshot change rate is about 2-3\% on average.
%All data are divided into 2 MB fix-sized segments and 
The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
%Each segment is divided into 
%variable-sized content chunks with an average size of 4KB.
%Popularity of data blocks are collected through global counting and 
%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.

@@

Our results show that VC has a significantly  higher availability than VO as the number of
failed machines increases from 3 to 20
in this table.
%Our VM-centric approach shows significant improvements
%in VM availability.
With $p=100$ and 3 machine failures,
there are 2500 VMs in total. VO with 69.5\% availability could lose data in 763 VMs 
while VC with 99.7\% loses data for 8 VMs.
The key reason is that for most data in VC, only a single VM can be affected by
the loss of a single file block. Since most blocks contain chunks for a single
VM, VMs can depend on a smaller number of blocks, while in VO, the loss of a
single block tends to affect many VMs.
When the number of physical machines failed reaches 20, the availability of VO reaches 0\%
and VC also drops to 1.13\%. This is because even there is a good availability for PDS data, VC still
loses most of non-PDS blocks given the replication degree for non PDS is 3.
On the other hand, when $p=1000$, the pecetnage of machine failure is then 2\% and
 VC outperforms VO significantly in availabilty in this case by delivering a meaningful avaiability with 99.62\%.

% because our VM-centric approach
%localizes deduplication.

%Although the loss of a PDS block affects many VMs,
%by increasing replication for those blocks we minimize the effect on VM
%snapshot availability, and this is one of the key contributions of our
%approach, the clear separation of highly popular data from less popular data.

%By having extra replicas for the PDS data, we reduce the failure rate of PDS
%FSBs enough that the failure rate for the VM approaches the failure rate of the
%Non-PDS blocks. This minimizes the drop in availability between the expected
%and worst case for VC.
%
%One of the advantages of VC is that there is a division between
%popular and non-popular data to facilitate improved reliability. 
Figure~\ref{fig:pds-replication} shows
the impact of increasing PDS data replication degree. 
While the impact on storage cost is small (because we have separated out only
the most popular blocks),
a replication degree of 6  has a significant improvement over 4. The
availability does not increase much  when increasing
$r_c$ from 6 to 9 and the benefit is not so visible after $r_c>9$. 
That is because when the number of failed machines increases beyond 6, 
the non-PDS data availability starts to deteroriate significantly given its replication degree
$r$ is fixed as 3. Thus when $r=3$, the reasonable choice for $r_c$ would be a number between 6 and 9.

@@

\begin{table}
  \centering
    \footnotesize
    \tabcolsep=0.11cm
    \pgfplotstabletypeset[
        comment chars=!,%use ! before a row in the data table to exclude it
        columns={NodesFailed,VO100,VC100,VO1000,VC1000},
        columns/NodesFailed/.style={
            column name={\multirow{3}{*}{Failures ($d$)}}
        },
        columns/VO100/.style={
            column name={
                \multicolumn{4}{c|}{VM Snapshot Availability(\%)}\\&
                \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
            VO},
            fixed, precision=6
        },
        columns/VC100/.style={
            column name={VC},
            fixed, precision=6},
        columns/VO1000/.style={
            column name={VO},
            fixed, precision=6},
        columns/VC1000/.style={
            column name={VC},
            fixed, precision=6},
        every head row/.style={
            before row={\hline},
            after row={\hline},
        },
        every last row/.style={after row=\hline},
        column type/.add={}{|},
        every first column/.style={column type/.add={|}{}},
        %the below rows can be used to extract rows 3,5,10,20 from rows 0-40
        %skip rows between index={0}{3},
        %skip rows between index={4}{5},
        %skip rows between index={6}{10},
        %skip rows between index={11}{20},
        %skip rows between index={21}{41}
    ]{figures/availability_table.txt}
    \caption{Availability of VM snapshots for VO ($r=3$) and VC ($r_c=6$, $r=3$).}
    \label{tab:vm-availability}
\end{table}

\begin{figure}[htb]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=10,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{
                    VO,
                    $r_c=4$,
                    $r_c=5$,
                    $r_c=6$,
                    $r_c=9$
                }
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees on a $p=100$-node cluster.}
  \label{fig:pds-replication}
\end{figure}

\subsection{Competitiveness of Deduplication Efficiency}
\label{sect:evaldedup}

\comments{
\begin{figure}[htb]
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                width=\linewidth,
                height=0.6\linewidth,
                ybar,
                bar width=0.5cm,
                ymax=98.7,
                enlarge x limits=0.15,
                style=thin,
                ylabel={Dedup. Efficiency (\%)},
                ytick={93,94,95,96,97,98},
                xtick=\empty,
                ymajorgrids,
                grid style=densely dotted,
                %symbolic x coords={VC-No PDS, VC-2\%PDS w/o similarity, VC-2\%PDS, VC-4\%PDS, SRB},
                %symbolic x coords={VC0, VC2N, VC2, VC4, SRB},
                %xticklabels from table={figures/efficiency_comparison_bars.txt}{alg}
                nodes near coords,
                every node near coord/.append style={
                    anchor=-145+\coordindex*10
                }
            ]
            %\addplot[fill=blue] coordinates {(VC0,93.02) (VC2N,94.31) (VC2,96.01) (VC4,96.58) (SRB,97.86)};
            %\addplot[fill=blue] coordinates { (VC-No PDS,93.02) (VC-2\%PDS w/o similarity,94.31) (VC-2\%PDS,96.01) (VC-4\%PDS,96.58) (SRB,97.86) };
            \addplot [%
                point meta=explicit symbolic,
                fill=blue
            ] table [x expr=\coordindex, y=efficiency,meta=alg] {figures/efficiency_comparison_bars.txt};
        \end{axis}
    \end{tikzpicture}
    \caption{Efficiency comparison between different VC settings and
        Stateless Routing with Binning}
    \label{fig:efficiency-comparison}
\end{figure}
}

\comments{
alg     efficiency
\scriptsize{}VC-2\%\tiny{}No\ Similarity        94.3132243792193
\scriptsize{}VC-NoPDS   93.0202119345744
\scriptsize{}VC-2\%PDS  96.0127647380588
\scriptsize{}VC-4\%PDS  96.5784837160482
\scriptsize{}SRB        97.8625610883421
}
\begin{table}
\begin{small}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
     \multicolumn{4}{|c|}{VC}  & VO \\ \hline
     2\%PDS  &  No PDS &2\%PDS     & 4\%PDS & SRB  \\ 
     no-simi&   &&  &    \\ \hline
     94.31\%& 93.02\%  & 96.01\% & 96.58\% & 97.86\% \\ \hline
    \end{tabular}
\end{small}
    \caption{Deduplication efficiency for different VC settings and
        Stateless Routing with Binning (SRB).}
    \label{tab:efficiency-comparison}
\end{table}

Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency for SRB and VC with different 
settings
and
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
duplication efficiency is defined as the percent of duplicate chunks which are removed
compared to a perfect scheme which detects and removes  all deduplicates. 
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
Notice $\sigma$ is the percentage of unique chunks selected in PDS.
With $\sigma =2\%$, Column 3 shows its 
%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
deduplication efficiency can 
reach over 96\%.
When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
more index space is allocated  per machine for  PDS fingerprint lookup.
% increases from 100MB to 200MB per physical machine as discussed later. 
%and  the deduplication efficiency can reach 96.489\%.
%When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
with a slight reduction in deduplication efficiency.

@@

Column 2 of Table~\ref{fig:efficiency-comparison} shows deduplication efficiency of VC without 
using PDS and it achieves 93.02\%, missing about 3-3.56\% of the original data. That is losing upto
356GB per physical machine because every machine deals with about 10TB data of snapshots. 
Column 1 of Table~\ref{fig:efficiency-comparison} shows deduplication efficiency of VC without 
local similarity search.
%There is a big efficiency drop in this curve when the number of VMs is about 30.
The reason similarity search provides such an improvement is that
%Without this (i.e. when we only 
there are VMs in which
data  segments are moved to another location on disk, for example when a file is rewritten
rather than modified in place,  
and a dirty-bit or offset-only based detection would not be able to detect such a movement.
We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently.
In general, adding local similarity-guided search increases deduplication efficiency from 94\% to over 96\%.
That is one significant improvement compared to the work in ~\cite{WeiZhangIEEE}
which uses the parent segment at the same offset to detect duplicates instead of similarity-guided search.
% In general, our experiments show that
% dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
% which leads about a 75.86\% reduction.
% Similarity-guided local search can further reduce the data size
% to about 12.05\% of original size, namely it delivers an additional 12.09\% reduction.
% The PDS-based global duplicate detection with $\sigma=2\% $
% can reduce the size further to 8.6\% of original size, namely it 
% delivers an additional 3.45\% reduction.

In general, our experiments show that
version detection at the segment level can reduce the data size to about 24.14\% of original data, 
which leads to about a 75.86\% reduction. Namely 10TB snapshot data per machine is reduced to 2.414TB.
Similarity-guided local search can further reduce the data size
to about 12.05\% of original, namely it delivers a 50.08\% reduction to the dirty segments.
The popularity-guided global deduplication with $\sigma=2\% $
can reduce the data further to 8.6\% of its original size and namely the final snapshot data size per machine
is reduced to 860GB, so it provides additional 28.63\% reduction to the remaining data.

@@

\begin{table}
\begin{small}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Tasks & CPU & Mem &Read &  Write  & Backup Time  \\ 
    & & (MB)          &(MB/s) &  (MB/s) & (hrs) \\ \hline
%    1     & 19\% & 118.1 & 50MB/s 8.37 & 1.314\\ \hline
    1     & 19\% & 118 & 50 & 16.4 & 1.31\\ \hline
%    2     & 35\% & 131.8 & 9.0 & 1.226\\ \hline
    2     & 35\% & 132 &50  & 17.6 & 1.23\\ \hline
    %4     & 63\% & 154.1 & 9.3 & 1.179\\ \hline
    4     & 63\% & 154&50   & 18.3 & 1.18\\ \hline
    6     & 77\% & 171.9 & 50 &  18.8 & 1.162\\ \hline
%    8     & 82\% & 90.5 & 89.2 & \\ \hline
%    10                      & 85\% & 97.2   & 90.4 \\ \hline
%    12                      & 91\% & 95.6    & 91.5 \\ \hline
    \end{tabular}
\end{small}
\caption{Resource usage of concurrent backup tasks at each physical machine with $\sigma=2\%$.}
\label{tab:resource_usage}
\end{table}
